\documentclass[char]{TMFHope}
\begin{document}
\name{\cBoy{}}

This is your chance to prove yourself - to make something of your life. And make a life \emph{with} someone.

You were born on a space station to a single mother. It was \emph{the worst.} You didn't belong on some backwater station washing dishes your whole life. There was no money to send you off to school, but you did your best with online courses on ship repair while you worked a dead end job as a switchboard operator. Seriously, how does a station that has a manual switchboard even deserve to be in orbit? Both you and your mother hoped that one day you could hire on to a ship and get out of there. 

One night while searching an obscure forum looking for something to help with your homework, you met \cNav{}. The two of you started exchanging messages, then talking regularly. \cNav{\They} \cNav{\are} quite terrific in many ways, and your dreams of getting off that dead-end station started to include joining up with \cNav{} somehow and sharing endless adventures together as the best of friends.

Just a few weeks ago, your chance came. \cNav{} messaged you with great news. The ship \cNav{\they} \cNav{\are} working on, the \pNew{}, was headed for your port. The two of you hatched a plan. Once the ship docked, \cNav{} dragged the crew to the bar where you were working (busing tables, ugh!) On a whim, you struck up a conversation with \cEng{}. Best decision of your life. \cEng{\They} \cEng{\are} a genius with a wrench, and what's more, \cEng{\they} saw something in you. \cEng{\They} went straight to the Captain the next morning and got you hired. \cNav{} barely had to do anything to try to help.

So began your new life aboard the \pNew{}. Seeing \cNav{} in person, every day, has been so wonderful. \cEng{} is an amazing mentor, but it didn't take you long to figure out \cEng{\they} \cEng{\are} losing \cEng{\their} sight. You know \cEng{\they}'d lose \cEng{\their} job if anyone found out. So you are covering for \cEng{} until you can think of something else. If only \cEng{} didn't despise \cNav{}, you are sure \cNav{} could think of a way to help. What's that even about?

The only sore spot until now was the military discipline with which the Captain and Executive Officer sometimes run the ship. It comes and goes in phases, and they feed off each other. Every time it happens, you want to take \cNav{} and abandon ship. But \cEng{} would never leave the \pNew{}, and you can't abandon \cEng{\them} either.

Now, of course, everything is terrible. The ship is trapped in the middle of a jump somehow, and don't seem to have access to the same places as \cEng{}. Will you be able to fix your parts of the ship without \cEng{\them}? Will \cEng{\they} be able to fix \cEng{\their} parts without you?


\subsection*{Abilities}
\begin{tabular}{|p{2cm}|p{1.5cm}|p{9cm}|p{3.5cm}|} 
 \hline
 \textbf{Ability Name} & \textbf{Uses} & \textbf{Ability Details} & \textbf{Ability Effect (what others see)} \\ 
\hline 
 \aEngineering{\MYname} & Unlimited & \aEngineering{\MYtext} & \aEngineering{\MYeffect} \\ 
\hline
 \aNegotiation{\MYname} & 3 uses & \aNegotiation{\MYtext} & \aNegotiation{\MYeffect}\\ 
 \hline
\end{tabular}

\subsection*{Memory and Event Packets}
\begin{enumerate}
	\item \mPractice{\MYname}
	\item \mAlpha{\MYname}
	\item \mDeckHandOne{\MYname}
	\item \mRepairsTwo{\MYname}
	\item \mRepairsFour{\MYname}
	\item \mBroom{\MYname}
	\item \mLab{\MYname}
	\item \mPatient{\MYname}
	\item \mKitchen{\MYname}
	\item \mWeight{\MYname}
	\item \mTheater{\MYname}
	\item \mCrates{\MYname}
\end{enumerate}

\begin{itemz}[Goals]
	\item Help \cEng{} fix the \pNew{}.
	\item Make sure no one finds out \cEng{} is losing \cEng{\their} sight.
	\item Help \cNav{} if they need it.
	\item Figure out why \cEng{} doesn't like \cNav{} and get them to reconcile. It's hard to have your two favorite people at odds.
\end{itemz}

\begin{itemz}[Notes]
	\item You start game in the Med Bay in the ``magenta'' dimension. You also have access to the Storage Bays in the ``Black'' dimension.
	\item The two dimensions you can access {\em feel} different somehow -- magenta feels purer, more primary, while black feels half-real, halfway between other dimensions, more secondary.  Is that how everyone else feels?
\end{itemz}

\begin{contacts}
	\contact{\cNav{}} Your platonic life partner. \cNav{\They} helped you get this job.
	\contact{\cEng{}} Your friend and mentor. \cEng{\They} \cEng{\are} teaching you to be a ship's engineer.
	\contact{\cCap{}} You dislike \cCap{\their} rigid military style. Doesn't \cCap{} know \cCap{\they} \cCap{\were} discharged? So bossy!
\end{contacts}

\end{document}
