\documentclass[char]{TMFHope}
\begin{document}
\name{\cCap{}}

Your name is \cCap{\full}. You {\bf were} \pTMN{}'s rising star, and now you are\ldots nothing? You're trying to start a new life on the \pNew{}, but it seems your past won't let you leave it behind. 

You were the captain of the \pOld{}, one of the Navy's best strike ships, and \cXO{\full} was your second in command. The two of you made a great complement. You are the calm and patient sort, and \cXO{} never hesitated to raise \cXO{\their} voice to get the crew to hop to. You'd gone through Officer's Academy together, and you kind of thought you could handle anything as long as you were together. It never seemed to matter that \cXO{} came from a \pEdge{} family and you from a \pPlan{} family. Even after the war broke out, \cXO{\they} fulfilled \cXO{\their} duties to you and the ship with honor, competence, and zeal. 

When the call to arms for went out for \pBattle{}, somehow the \pOld{} didn't receive it. It wasn't until hours later that the  missive came through on coms. By the time you jumped in, the battle was lost - or so any tactician would have said. But that was your home planet of \pHome{} below, so the \pOld{} went to battle stations and waded in. Your ship was out-matched; the move was suicide. But you had a secret weapon. You pulled a medallion from around your neck - an old family heirloom - and smashed it on the floor of the Bridge. Smoke poured from the broken bits of glass and metal, and a voice of something ancient and malevolent spoke to you. You begged for the power to turn the tide of battle and save your planet. The entity agreed, and vanished. The price would come clear in time.

The \pOld{} \emph{did} carry the day. You scraped a miraculous win. Despite this, your superiors were obligated to issue a dishonorable discharge for your failure to answer the summons in a timely manner. You spiraled out for a while - your family had been in the Navy for generations. Your mother, her parent, their father, numerous aunts, uncles, and several niblings\ldots you get the picture. You drifted from station to station, directionless. One night you got into a fight over a game of cards, and the cheating bastard drew a knife. If it weren't for \cSci{} and \cMed{}, you might have died in that back room. \cSci{}, another player at the table joined the fight, but it was not particularly clear whose side \cSci{\they} \cSci{\were} on. They only seemed interested in a jolly fight. The bastard with a knife got one good cut down your side before the barkeep broke the fight up - you might have died of blood loss, but \cMed{} patched you up, whether you deserved it or not. You owe \cMed{} and possibly \cSci{} your life.

A brush with death like that will knock some sense into even the stubbornest \cCap{\human}. You began to pick up the pieces of your life. You reached out to \cXO{}, who had told you when you were discharged that if you ever needed anything you need only ask. You'd never command another military ship, but plenty of merchant craft needed captains. \cXO{} helped you secure one, the \pNew{}, and then to your amazement, quit their position in the Navy, and came to serve on your crew. \cMed{} and \cSci{}, who you'd been keeping in touch, with were also surprisingly happy to leave their station-side posts to join up. If your grandfather was still talking to you, he'd tell you that it was a sign of your leadership. \cEng{} came with the ship - and that was a piece of luck. \cEng{\They} \cEng{\are} the best in the business. Or \cEng{\were}, before \cEng{\their} eyesight started to go. \cEng{} tries to keep it hidden (and \cEng{\they} \cEng{\are} still a hell of an engineer), so out of respect you've kept quiet that you've noticed. The rest of the crew of the \pNew{} assembled in bits and pieces, and now you've got a full complement and a couple of months experience working together. Things are looking up.

Except for the dreams. The dreams started the night after \pBattle{}. You are haunted by ghosts who scream and cry in pain; ghosts from \pPlan{} ships, good crewmembers who died in that battle. This is the price you pay for your miracle.	A week ago, you started seeing the ghosts even during your waking hours. At first it was just in quiet moments when you were alone and your thoughts drifted, but it becomes more frequent with each passing day. You are trying desperately to keep it together. If the wrong person found out you were seeing ghosts, you could be declared unfit for command. But everyone must have confidants. You've taken a huge risk and told \cMed{} and \cSci{} (separately of course), and while it didn't make the ghosts go away, it has helped steady you to be able to handle this crisis. After having a few days to think about it, you aren't sure that was a good idea, and have resolved not to talk about it any more, at least until the current crisis is resolved. Unless they are somehow connected? Still, it is probably not a good thing to bring the ghosts up again unless pushed for it. Even with the people you've already told. What if someone were to overhear?

As you wake up on the bridge of the \pNew{}, everything is cast in a yellow hue. As the Captain, you have a responsibility to your crew, and may have to set your personal problems aside for it. Still, peace from the ghosts after 6 years of this would be a blessing. Surely this is \emph{somebody's} fault, and hopefully not yours. 

\subsection*{Abilities}
\begin{tabular}{|p{3cm}|p{1.5cm}|p{8cm}|p{3.5cm}|} 
 \hline
 \textbf{Ability Name} & \textbf{Uses} & \textbf{Ability Details} & \textbf{Ability Effect (what others see)} \\ 
\hline
 \aTruth{\MYname} & 3 uses & \aTruth{\MYtext} & \aTruth{\MYeffect} \\
\hline
 \aCalculate{\MYname} & Unlimited & \aCalculate{\MYtext} & \aCalculate{\MYeffect} \\ 
 \hline
\end{tabular}

\subsection*{Memory and Event Packets}
\begin{enumerate}
	\item \mPractice{\MYname}
	\item \mCAlpha{\MYname}
	\item \mCaptainOne{\MYname}
	\item \mCaptainTwo{\MYname}
	\item \mBroom{\MYname}
	\item \mLab{\MYname}
	\item \mPatient{\MYname}
	\item \mKitchen{\MYname}
	\item \mWeight{\MYname}
	\item \mTheater{\MYname}
	\item \mCrates{\MYname}
\end{enumerate}

\begin{itemz}[Goals]
	\item Repair the \pNew{}.
	\item Find out who is responsible for the botched Jump and bring them back to \pHome{} for a full investigation.
	\item Keep crew morale up, and keep everyone working as a team.
	\item Try to prevent anyone from dying. Depending on the exact nature of the damage to the ship, it may not be possible to save everyone - in which case, you may be called upon to decide who to leave behind.
\end{itemz}

\begin{itemz}[Notes]
	\item You start on the Bridge in the ``Yellow'' Dimension. You also have access to the Gym in the ``Green'' Dimension. 
	\item The two dimensions you can access {\em feel} different somehow -- yellow feels purer, more primary, while green feels half-real, halfway between other dimensions, more secondary.  Is that how everyone else feels?
	\item You know that the \pNew{} has very limited supplies for repairing the ship or any unorthodox operations to try to reverse whatever happened. It is vital that you get a full inventory of what damages the ship has sustained, what will be required to repair it, and establish a plan, {\bf before} anyone starts trying to repair anything.
\end{itemz}

\begin{contacts}
	\contact{\cXO{}} Your oldest friend who served in the war with you.
	\contact{\cMed{}} The Doctor who saved your life, and whom you've told about the ghosts. You get along well even though \cMed{\they} \cMed{\are} quite introverted.
	\contact{\cSci{}} Another player at the card table who may or may not have saved your life. You've told \cSci{\them} about the ghosts. \cSci{\They} \cSci{\are} cheerful and curious, but surprisingly ready to throw down - apparently for the fun of it; you get along well.
	\contact{\cBoy{}} You brought the \cBoy{\kid} aboard against your better judgment. If \cEng{} didn't need help, and the two of them hadn't hit it off so wonderfully, you would have refused. Could \cBoy{} be responsible for the botched Jump?
\end{contacts}

\end{document}
