\documentclass[char]{TMFHope}
\parindent=0pt
\begin{document}
\name{\cDip{}}

You are a diplomat - for the moment. \cDip{} still feels like a bad fit, but it's the name you were given for a previous assignment, and you're stuck with it - for now. You've played diplomat before, now you have to play it again. If it weren't for that incident on \pHome{} three years ago with \cWeap{}, you would be sneaking around some corporate headquarters or King's bedchamber. Instead you're stuck on this good-for-nothing rust bucket, keeping an eye on \cXO{} for the \pPlan{}. You are so much better than these people, and you do your best to look, act, and dress like it. The rest of the crew must never be allowed to forget your superiority.

Dump heap assignment or not, you don't intend to let your skills dull out here. The favor of your superios is fickle and you'll be back on the up and up soon enough. It's a game to find blackmail on as many crewmembers as possible. \cMed{} is the one exception to your game. You grew up on the same space station as \cMed{\them}. Something about \cMed{their} hopeless nerdiness disarms your usual desire to manipulate and blackmail people. You were kind to \cMed{\them} growing up, and \cMed{\they} to you. You suppose that makes you friends of sorts. You wouldn't throw your career away for \cMed{\them} - you surely have no such sentimental attachments, right?\ldots right? But if \cMed{} needed help and it wouldn't compromise your position, you suppose you could assist.

It's also a game to \emph{tease} people that you know what you know. \cXO{} is particular fun to mess with. \cXO{\They} is understandably unhappy that you know \cXO{\they} are responsible for the failure of \pOld{} to report for battle. Which is supposedly why you are keeping an eye on \cXO{\them}. \cXO{} is from an old \pEdge{} family that is starting to stir up trouble again. \cXO{\They} played such a key part last time, your superiors want no such surprises this time. You won't tell anyone of course, unless it becomes necessary to save your own skin - after all, blackmail only works by the \emph{threat} of reveal. Still, it's been delightful to watch \cXO{} be particularly jumpy the past week or so. 

\cWeap{} is an {\bf unwelcome} blast from your past. \cWeap{} was assigned as your bodyguard on that fateful mission three years ago. It's not like you can't take care of yourself, but appearances must be maintained and a \emph{diplomat} shouldn't be able to protect themselves. So you had that meat-head in tow. And then your target did \emph{something} - you are still not sure what, and \cWeap{} shot them. It was a diplomatic nightmare - and more importantly scuttled your mission. And now \cWeap{\they}'s here, on \pNew{}, with you. What did you ever do to deserve this?

\begin{itemz}[Goals]
	\item Make \cWeap{} look bad. End \cWeap{\their} career if you can.
	\item Figure out who caused this awkward mess with the Jump, and get it fixed - you would like to go home. Maybe \cXO{} has been so twitchy because they planned this?
	\item Help \cMed{} out if they need it - they seem to be the one person here who properly likes you.
	\item Find blackmail on as much of the crew as possible, just in case.
	\item Handle any potential First Contact situations. - Not that you remotely expect that possibility (you don't actually believe there -are- any other sentient species in the universe), but it is ostensibly your \emph{job} as the Diplomat. And it would be fun to run the ship for a while and string everyone along - the Diplomat outranks even the Captain in a First Contact scenario.
\end{itemz}

\begin{itemz}[Notes]
	\item You start on the Bridge in the ``Yellow'' Dimension. You also have access to the Storage Bays in the ``Black'' Dimension. 
	\item You are inclined to be suspicious of any supposed first contact situation, but it would be fun to fake it for a while if the opportunity arose.
\end{itemz}

\begin{contacts}
	\contact{\cXO{}} You know what \cXO{\they} did in the war. Gloating about it where no one else can hear is fun.
	\contact{\cMed{}} You grew up with \cMed{\them}. You are friends you guess.
	\contact{\cWeap{}} - Your former bodyguard whose trigger happy nature got you in trouble with your superiors.
\end{contacts}

\end{document}
