\documentclass[char]{TMFHope}
\begin{document}
\name{\cEng{}}

You grew up on ships. Your parents were ship's engineers. You learned to fix ships almost before you could walk. You've worked on \pNew{} your entire adult life. In many ways, she's your baby. You are the crew-member who has served aboard her for the longest. \cCap{} is your third captain, and for the most part is a fine Captain. Nothing too extraordinary. They run the ship tighter than you would, but hey, it's not so tight that you can't just shrug it off and go about your job.

In the decades you have worked on ships, you've seen drastic improvements in space travel. You remember a time when the jump drives couldn't be within 50 feet of a magnet or they'd go haywire - that was before proper shielding was developed. And you remember the fireworks when someone tried to use their jetpacks to propel themselves around the outside of the ship during an emergency repair in the middle of flammable dust cloud - that was before space suits had non-combustion based jet packs. You remember your parents telling you about early grav-boot technology, before the grav fields were developed. On the bigger ships and stations, people would regularly walk on the ceiling as well as the floor, and bonk heads with each other until everyone learned to lean left if you were on the ground or right if you were on the celing to pass! You remember your first Captain demanding you make the ship go to ``Warp 10'', whatever that was supposed to mean - too many sci fi shows, not enough real experience on a ship. You remember a lot of things.
 
The Ship's doctor, \cMed{}, has taken an interest in your stories. \cMed{\They} seem to think that they would make a good memoir. It is hard for you to believe that anyone would care about the stories a transport ship's engineer could tell. Still, \cMed{} seems earnest, and you haven't yet outright refused to give them permission to help you write and publish a memoir. You've even let them record a couple of your stories in preparation for such a thing. There is another reason you don't want the doctor hanging around too much though\ldots

You are, unsurprisingly, the oldest member of the crew. Old enough that your body aches in the morning, and your eyesight is going. For several years you were able to conceal the matter with contacts, and then glasses, but now you are bordering on blind. You are terrified of \cCap{} or even worse, \cXO{} finding out - you'd surely be dismissed from the crew. And of course \cMed{} would  be obligated to tell them if \cMed{\they} found out. \cWeap{} is also a problem, always trying to stick \cWeap{\their} nose where it doesn't belong. You have to regularly throw \cWeap{\them} out of the engine room.

It was a stroke of luck meeting \cBoy{} at the last port of call. Despite never having been on a ship before, \cBoy{\they} seem\cBoy{\plural} to have an innate talent for taking care of the \pNew{}. \cBoy{} reminds you of yourself when you were younger. You went to \cCap{} and requested to add \cBoy{} to the crew first thing in the morning. \cCap{} was surprisingly easy to convince. You suspect it had to do with \cNav{} advocating for the same thing. You suppose you should be grateful to \cNav{\them} for that. But that's as far as your gratitude extends. \cNav{} is always talking about jump tech, and insinuating that \pNew{} could do so much more than she is already doing. Even if managing jumps weren't the navigator's job, you'd still suspect \cNav{} of being at fault for the current mess.

Your poor ship. She's trapped between dimensions or something, and it is tearing her apart. You've got to fix her, no matter what.

\subsection*{Abilities}
\begin{tabular}{|p{2.5cm}|p{1.5cm}|p{10cm}|p{2cm}|} 
 \hline
 \textbf{Ability Name} & \textbf{Uses} & \textbf{Ability Details} & \textbf{Ability Effect (what others see)} \\ 
\hline 
 \aEngineering{\MYname} & Unlimited & \aEngineering{\MYtext} & \aEngineering{\MYeffect} \\ 
\hline
 \aEyesight{\MYname} & Always Active & \aEyesight{\MYtext} & \aEyesight{\MYeffect}\\ 
 \hline
	\aPractice{\MYname} & Unlimited & \aPractice{\MYtext} & \aPractice{\MYeffect} \\ 
\hline
\end{tabular}

\subsection*{Memory and Event Packets}
\begin{enumerate}
	\item \mPractice{\MYname}
	\item \mEAlpha{\MYname}
	\item \mEngineerOne{\MYname}
	\item \mRepairsOne{\MYname}
	\item \mRepairsThree{\MYname}
	\item \mRepairsFive{\MYname}
	\item \mBroom{\MYname}
	\item \mLab{\MYname}
	\item \mPatient{\MYname}
	\item \mKitchen{\MYname}
	\item \mWeight{\MYname}
	\item \mTheater{\MYname}
	\item \mCrates{\MYname}
\end{enumerate}

\begin{itemz}[Goals]
	\item Fix the \pNew{}, no matter what.
	\item Prove that \cNav{} caused this botched jump and make sure \cNav{\they} can't do it again.
	\item Teach \cBoy{} how to be a good engineer.
	\item Decide if you are going to let \cMed{} record your stories, and decide if you will let them publish a memoir about your life.
	\item Don't let anyone figure out that your eyesight is going.
\end{itemz}

\begin{itemz}[Notes]
	\item You start game in the Science Lab in the ``Cyan'' dimension. You also have access to the Gym  in the ``Green'' dimension.
	\item The two dimensions you can access {\em feel} different somehow -- cyan feels purer, more primary, while green feels half-real, halfway between other dimensions, more secondary.  Is that how everyone else feels?
\end{itemz}

\begin{contacts}
	\contact{\cBoy{}} Space is hard enough for those who grew up in it. \cBoy{} grew up station side. You've been helping \cBoy{\them} learn the ropes.
	\contact{\cWeap{}} \cWeap{} is nosy, and you are worried \cWeap{\they} will discover your eyesight is failing.
	\contact{\cMed{}} \cMed{} is convinced that the world needs to hear your story. While that's very sweet of \cMed{\them}, you are worried \cMed{\they} will discover your eyesight is failing.
	\contact{\cNav{}} \cNav{\They} \cNav{\are} the newest crew-member \(aside from \cBoy{}\). Your ship never failed a jump before \cNav{\they} came aboard. The navigator is in charge of jumps. This is \cNav{\their} fault, you just have to prove it. And then get them off your ship!
\end{contacts}

\end{document}
