\documentclass[char]{TMFHope}
\begin{document}
\name{\cMed{}}

You grew up on a space station with \cDip{\full}. You were never terribly close confidants, as \cDip{\their} patience for talk about technology was limited, but \cDip{\they} always showed you a softer side than \cDip{\they}showed anyone else. Still, as you grew older, you drifted apart. \cDip{} went into political science, and you pursued a career in medicine. Eventually you found yourself practicing on a small space station not unlike the one you grew up on. One would think such a life quiet, but as any port on a shipping line can attest, the number of bar-brawls could keep twice as many doctors busy.

One night, \cSci{\full} walked through your door as you were closing up. You assumed \cSci{\they} needed patching up, as \cSci{\they} \cSci{\were} splattered with blood, but for once \cSci{\their} propensity for ``jolly fights'' seemed to have helped someone instead of just causing trouble. \cSci{\They} brought you \cCap{\full}, with a bad knife wound along \cCap{\their} side. You were at it all night saving \cCap{\their} life. It wasn't until days later that you learned that you'd operated on the hero of \pBattle{}.

You and \cSci{} joked about it for months. Your casual acquaintanceship grew into a serious friendship, and friendly rivalry. \cSci{} could \emph{almost} keep up with you at your nerdiest, and you spent endless, delightful hours debating the latest science and theory. When \cCap{} reached out to you about a job on \pNew{}, you were happy to join up. Surely a ship with a crew of only 9 would be quieter than working the station. And your friend \cSci{} was joining up too. How lovely.

Things went smoothly for a couple of months, but just under a week ago, the Captain came to you with a fascinating and distressing revelation. \cCap{} is apparently seeing ghosts or apparitions of some kind, and has been for a while. \cCap{\They} called it ghosts, but you aren't so sure. What if the Captain is somehow being reached by sentient beings and doesn't realize it because they are so different from us? If only you could see one for yourself\ldots

This business with the \pNew{} is very bad. You woke up to everything in a strange, cyan tone. It seems your quiet stint on the ship is over - it is up to you to make sure everyone gets through this in one piece - physical and mental.

\subsection*{Abilities}
\begin{tabular}{|p{3cm}|p{1.5cm}|p{6.5cm}|p{5cm}|} 
 \hline
 \textbf{Ability Name} & \textbf{Uses} & \textbf{Ability Details} & \textbf{Ability Effect (what others see)} \\ 
\hline 
 \aInvestigation{\MYname} & Unlimited & \aInvestigation{\MYtext} & \aInvestigation{\MYeffect} \\ 
\hline 
\aFirstAid{\MYname} & 3 uses & \aFirstAid{\MYtext} & \aFirstAid{\MYeffect}\\ 
 \hline
\end{tabular}

\begin{itemz}[Goals]
	\item Keep the crew as healthy and safe as possible. This will be challenging as you can't seem to access the med lab, and only some of the crew is with you.
	\item Investigate the Captain's ``ghosts''. Maybe something about this unusual situation will give you the breakthrough you need to figure out what is going on.
	\item Help \cDip{} out. You don't think \cDip{\they} \cDip{\are} a bad person, but \cDip{\they} \cDip{\are} much better at making enemies than friends.
\end{itemz}

\begin{itemz}[Notes]
	\item You start in the Science Lab in the ``Cyan'' Dimension. You also have access to the Gym in the ``Green'' Dimension. 
\end{itemz}

\begin{contacts}
	\contact{\cCap{}} You saved \cCap{\their} life, and are trying to help \cCap{\them} with \cCap{\their} ``ghosts.''
	\contact{\cSci{}} Your friend / rival. \cSci{\They} \cSci{\are} almost as clever as you.
	\contact{\cDip{}} A childhood friend. You aren't really close anymore, but \cDip{\they} \cDip{\have} never been good at making friends and you like helping people.
\end{contacts}

\end{document}
