\documentclass[char]{TMFHope}
\begin{document}
\name{\cSci{}}

Life is a jolly ride. New adventures just seem to present themselves to you whenever your previous arrangements are starting to grow stale, and \pNew{} is just the next in a long string. You've got good friends, and a good life, here. Whatever happened with this jump is most upsetting as it threatens what was otherwise a perfect life.

You've always drifted with the aether currents. First you wandered to the best University on \pHome{}, and got a prestigious science degree (what, like it's hard?). There you met \cXO{\full}, with whom you had a wonderful romance. Next, rather than immediately getting some corporate job, you took a tour of the seediest, most backwater \pEdge{} planets, where you learned to gamble and brawl with the best of them. Next you drifted to the space station where you finally took that high paying corporate job your parents wanted you to, and met \cMed{\full}. You were in and out of \cMed{\their} practice all the time - you never could resist a jolly fight - but you didn't really get close until \cCap{\full} near about got \cCap{\themself} killed over a little card game. So of course you just had to step in and help \cCap{\them} out. You backed \cCap{} in the fight, and then took \cCap{\them} to \cMed{} after \cCap{\they} took a knife to the side despite your best efforts. 

After that day, you and \cMed{} became fast friends. Your casual acquaintanceship grew into a serious friendship, and friendly rivalry. \cMed{} could \emph{almost} keep up with you at your nerdiest, and you spent endless, delightful hours debating the latest science and theory. When \cCap{} reached out to you about a job on \pNew{}, you were happy to join up. It'd make a nice change.

The great surprise was of course the Executive Officer (XO). The second mate on the \pNew{} is \cXO{}, your old college flame. It was such a pity when \cXO{\their} family ordered them into the military. You'd lost touch, but maybe this was your chance to reconnect. Just the pesky little problem of romance being forbidden between crew-members. Still, snatching secret minutes and quick kisses has been exhilarating.

Things went smoothly on the \pNew{} for a couple of months, but just under a week ago, the Captain came to you with a fascinating and distressing revelation. \cCap{} is apparently seeing ghosts or apparitions of some kind, and has been for a while. \cCap{\They} called it ghosts, but you aren't so sure. What if the Captain is somehow being reached by humans from a parallel universe? If only you could see one for yourself\ldots

In the mean time, this strange business with the \pNew{} possibly being stuck between dimensions is pretty exciting. Also scary, cause you and \cMed{} and \cXO{} might die. So you should probably get on helping fix that.

\subsection*{Abilities}
\begin{tabular}{|p{3cm}|p{1.5cm}|p{8cm}|p{3.5cm}|} 
 \hline
 \textbf{Ability Name} & \textbf{Uses} & \textbf{Ability Details} & \textbf{Ability Effect (what others see)} \\ 
\hline 
 \aInvestigation{\MYname} & Unlimited & \aInvestigation{\MYtext} & \aInvestigation{\MYeffect} \\ 
\hline
 \aEngineering{\MYname} & Unlimited & \aEngineering{\MYtext} & \aEngineering{\MYeffect}\\ 
 \hline
\end{tabular}

\begin{itemz}[Goals]
	\item Help and support \cXO{}. Probably easiest if you keep your relationship with \cXO{\them} a secret.
	\item Figure out how the jump went bad, and fix it.
	\item Investigate the Captain's ``apparitions.''  Maybe something about this unusual situation will give you the breakthrough you need to figure out what is going on.
\end{itemz}

\begin{itemz}[Notes]
	\item You start on the Bridge in the ``Yellow'' dimension. You also have access to the Recreation Room in the ``Red'' dimension.
\end{itemz}

\begin{contacts}
	\contact{\cXO{}} Your delightful romantic partner. 
	\contact{\cMed{}} Your good friend who is almost as clever as you.
	\contact{\cCap{}}You're helping \cCap{them} with their ``apparitions'' problem.
\end{contacts}

\end{document}
