\documentclass[char]{TMFHope}
\begin{document}
\name{\cXO{}}

You are \cXO{\full}. You served in \pTMN{} for several years alongside \cCap{\full}, then quit in hopes of escaping your family's meddling. 

You and the captain made a great complement. \cCap{} was the calm and patient sort, and you have never hesitated to raise your voice to get the crew to hop to. \cCap{} and you were very close in Officer's Academy, so when the war broke out, things got very awkward for you very quickly. Your family were \pEdge{}, and \cCap{} was from \pHome{}. Your family demanded you prove your loyalty by preventing the \pOld{} from receiving the summons to \pBattle{}. Reluctantly you sabotaged the \pOld{} com system, and delayed its repair for as long as you could. With the hours-long delay, \pOld{} was in no position to help when she jumped in over \pHome{}, but \cCap{} sent everyone to battle stations and waded in anyway. You knew you were going to die on that suicide mission. But something happened - suddenly the bridge of the \pOld{} was filled with choking smoke. Then it was gone. From that moment on, the \pOld{} and her crew could do no wrong in that battle. You did the impossible that day.

The few survivors of your family were furious, but with the back of the \pEdge{} broken, they could do nothing more than forbid you to take the fall for \cCap{}. \cCap{\They} \cCap{\were} given a dishonorable discharge, and you lost track of \cCap{\them} for a few years. When \cCap{\they} resurfaced, and asked you for help getting a civilian command, you jumped at the chance. You helped \cCap{} acquire the \pNew{}. Then, tired of your family's meddling, you quit the Navy and signed on as \cCap{}'s XO. You never wanted to betray \cCap{\them}, but betray you did, and you shudder to think what would happen if \cCap{} ever found out.

As you helped \cCap{} assemble a crew for the \pNew{}, an old, familiar name came up for the position of Scientist. You went to college with \cSci{} before joining the Officers Academy. The two of you had a powerful romance, and it broke both of your hearts when you family ordered you to the Academy. You tried to tell yourself that it was years ago, and that \cSci{} had probably moved on. You tried to tell yourself that it would be against regulations to try to rekindle what the two of you had. You tried to tell \cCap{} that \cSci{} wasn't the best candidate. None of it worked. Within a week of \cSci{} joining the crew, the two of you were stealing time alone whenever you could. Yet another secret to desperately try to not get caught for. It was drilled into you at the academy: No romance or platonic life partner relations between crew members in the same chain of command; the power dynamic makes it impossible for it to be ethical - and sometimes people ignore orders and do something that puts the whole ship in jeopardy to save a partner. You tell yourself you'd never do that. You can be both a good Executive Officer, and a good partner - you tell yourself that you'd do your duty, even if it meant sacrificing \cSci{} for the rest of the crew. You tell yourself a lot of things.

Not everyone on the crew is an old friend. \cDip{} is an old family enemy. \cDip{\They} used to be a spy - you aren't sure that \cDip{\they} \cDip{\are}n't still a spy. \cDip{\They} \cDip{\were} a spy for \pPlan{} before and during the war. And somewhere in all of that \cDip{\they} claim\cDip{\plural} to have ferreted out what you did to \cCap{} on the \pOld{}. \cDip{} holds that blackmail over you, gloating whenever the two of you are alone. So far \cDip{\they} \cDip{\have}n't asked you to do anything in exchange for \cDip{\their} silence, but how long will that last? You've got to do something to neutralize \cDip{\them}. And \cDip{} is nosy. You are increasingly paranoid that \cDip{\they} might find out about you and \cSci{}.

Maybe you can find a way to make \cDip{} so miserable \cDip{\they} quit on \cDip{\their} own? Or maybe you can find evidence \cDip{\they} \cDip{\are} unfit for \cDip{\their} position somehow? After all, it is the XO's job to report on the fitness of the crew. Even though \pNew{} is a civilian ship, since the diplomat is assigned by the government, you have a clear way to get \cDip{them} off your ship. All you need is proof. And maybe you've been a little lax in assessing the crew's fitness. After your time in the Navy, being on a civilian ship just felt so relaxed in comparison. You hadn't really imagined something like this happening. But now you've got a major crisis on your hands, and if everyone isn't physically, mentally, and emotionally prepared for it, you might all die. You are resolved to prepare a report for the \pNew{}'s parent shipping company to submit at the next available upload point (your next port of call.) You plan to reward extraordinary effort, and be honest about any shortcomings. Your report could start - or end - a career for a crew member.

As you wake in the Med Bay, everything has a magenta tint.  As the XO, it is your job to support the Captain, protect the crew, repair the ship, and get home. Of course this all depends on finding out who is responsible. Something like this is no laughing matter - people could die. And you don't trust \pPlan{} justice. After all, they produce people like \cDip{}. You'd rather deal with this yourself, out here on the edge of space. Tragic accidents happen all the time - no one said traveling in space was safe - and that way whoever it is won't get away with nearly killing 8 people by looking cute and spinning some stupid lie.

\subsection*{Abilities}
\begin{tabular}{|p{3cm}|p{1.5cm}|p{8cm}|p{3.5cm}|} 
 \hline
 \textbf{Ability Name} & \textbf{Uses} & \textbf{Ability Details} & \textbf{Ability Effect (what others see)} \\ 
\hline 
\aThreat{\MYname} & Unlimited & \aThreat{\MYtext} & \aThreat{\MYeffect} \\ 
 \hline
	\aPractice{\MYname} & Unlimited & \aPractice{\MYtext} & \aPractice{\MYeffect} \\ 
\hline
\end{tabular}

\subsection*{Memory and Event Packets}
\begin{enumerate}
	\item \mPractice{\MYname}
	\item \mXAlpha{\MYname}
	\item \mThreatOne{\MYname}
	\item \mThreatTwo{\MYname}
	\item \mThreatThree{\MYname}
	\item \mThreatFour{\MYname}
	\item \mBroom{\MYname}
	\item \mLab{\MYname}
	\item \mPatient{\MYname}
	\item \mKitchen{\MYname}
	\item \mWeight{\MYname}
	\item \mTheater{\MYname}
	\item \mCrates{\MYname}
\end{enumerate}

\begin{itemz}[Goals]
	\item Protect and support \cSci{}, and definitely don't let anyone find out about your relationship. It's a dismissible offense for you, and could ruin \cSci{\their} career.
	\item Find out who caused the botched Jump - honestly, it was probably \cDip{}. They've got it in for you. You don't trust \pPlan{} justice though - it's best if you deal with \cDip{\them} here and now.
	\item Protect the rest of the crew from the saboteur, whoever they are.
	\item Deal with \cDip{} somehow. Find blackmail on \cDip{\them}, neutralize what \cDip{\they} \cDip{\have} got on you, make sure \cDip{\they} \cDip{\does}n't survive this, or something. Enough is enough, you didn't escape your family just to be under this jerk's thumb instead.
	\item Evaluate the crew for general fitness. A crisis like this demonstrates exactly why everyone must be able to perform at their best. If you find out that anyone isn't able to perform their functions, you will have to decide if you report them and probably end their career, or keep quiet, and put this crew and whoever they may work with in the future at risk. The GM will ask you for your report at the end of game.
\end{itemz}

\begin{itemz}[Notes]
	\item You start in the Med Bay in the ``Magenta'' Dimension. You also have access to the Rec Room in the ``Red'' Dimension. 
	\item The two dimensions you can access {\em feel} different somehow -- magenta feels purer, more primary, while red feels half-real, halfway between other dimensions, more secondary.  Is that how everyone else feels?
\end{itemz}

\begin{contacts}
	\contact{\cCap{}} You regret betraying \cCap{} every day of your life.
	\contact{\cSci{}} You first met \cSci{} in college, before going to officers school. You had a romance then that you have rekindled on the \pNew{}. It is, of course, against regulations, and you would be in a lot of trouble if anyone found out.
	\contact{\cDip{}} Nosy pain in the neck, \cDip{} knows what you did during the war between the \pPlan{} and \pEdge{}. You hate being blackmailed like this.
\end{contacts}

\end{document}
