\documentclass[sheet]{TMFHope}

\usepackage{hyperref}

%% document-wide tweaks
\interlinepenalty10000
\setstretch{1}
\def\mytype{Rules and Scenario}
\lfoot{}\rfoot{}
\parindent0pt

\begin{document}

%% title box
\begin{center}\LARGE\bf\begin{tabular}{|c|}
  \hline \gamename\\ \gamedate\\ Dramatis Personae\\ \hline
\end{tabular}\end{center}


This is the crew-list for the \pNew{}.

\begin{itemize}
  \item \cCap{\full}, \cCap{\they}/\cCap{\them} (\cCap{\MYplayer}): The Captain of the \pNew{}. \cCap{\Theyare} are easy going and likeable. How \cCap{\they} manage\cCap{\plural} to simultaneously be everyone's friend and also maintain appropriate distance and impartiality is quite the trick. \cCap{\They} served in \pBattle{} on the \pOld{}, after which \cCap{\theywere} issued a dishonorable discharge.
  
  \item \cXO{\full}, \cXO{\they}/\cXO{\them} (\cXO{\MYplayer}): The Executive Officer of the \pNew{}. \cXO served in the \pPlan{} millitary with \cCap{}. \cXO{\They} left \cXO{\their} post to join the crew of \pNew{}. \cXO{\Theyare} a good foil to the Captain, being direct, businesslike, and at times even impatient with crewmembers who dawdle at executing orders.
  
  \item \cDip{\full}, \cDip{\they}/\cDip{\them} (\cDip{\MYplayer}): The Diplomat assigned to the \pNew{}. \cDip{\Theyare} prim and proper, always smiling a smile that doesn't quite reach \cDip{\their} eyes. A consumate diplomat, \cDip{\theyare} always polite, and seem\cDip{\plural} to hold everyone else at arm's length. Still, if you need advice on how to handle a social situation, there is no one better to advise you.
  
  \item \cMed{\full}, \cMed{\they}/\cMed{\them} (\cMed{\MYplayer}): The Doctor on the  \pNew{}. \cMed{\Theyare} responsible for keeping the crew whole and hale. \cMed{\They} take\cMed{plural} the responsibility quite seriously, and does a good job looking after the crew. \cMed{} is a little on the quiet side, maybe even awkward among folks \cMed{\theydo}n't know well.
  
  \item \cEng{\full}, \cEng{\they}/\cEng{\them} (\cEng{\MYplayer}): The Engineer who takes care of \pNew{}. \cEng{\Theyare} the best of the best, in part due to how long \cEng{\theyhave} been an engineer. It's anybody's guess what \cEng{\theyare} doing on a little ship like \pNew{} when \cEng{\they} could have \cEng{\their} pick of the fleet. Still, \cEng{} is the heart of the crew and the \pNew{} wouldn't be the same if \cEng{\theywere} ever to retire.
  
  \item \cWeap{\full}, \cWeap{\they}/\cWeap{\them} (\cWeap{\MYplayer}): The Weapons specialist of the \pNew{}. \cWeap{\Theyhave} a busy past, having served in the millitary, and then transfered to the secret service. Now \cWeap{\they} seem\cWeap{\plural} to just want to do their job minding the \pNew{} laser, usually used to blast asteroids out of the way, and forget \cWeap{\their} past. \cWeap{} get\cWeap{\plural} edgy if you ask too many questions.
  
  \item \cNav{\full}, \cNav{\they}/\cNav{\them} (\cNav{\MYplayer}): The Navigator of the \pNew{}. \cNav{\Theyare} in charge of piloting the ship and calculating jumps through hyperspace. While the \pNew{} navigator is fairly new at the job, \cNav{\they} graduated top of \cNav{\their} class and \cNav{are} considered an up and coming talent in the field. \cNav{} is, bubbly and friendly, an open fan\cNav{\kid} of \cCap{}, and an avid history buff. Don't get them started on the history of the war between \pPlan{} and \pEdge{}.
  
  \item \cSci{\full}, \cSci{\they}/\cSci{\them} (\cSci{\MYplayer}): The Scientist of the \pNew{}. \cSci{\Theyhave} a comparatively easy job on the ship, mostly just hanging around and being an extra pair of hands when things are running normally. If the \pNew{} runs into anything \emph{weird} though, a good scientist can be the difference between surviving and being space debris. \cSci{\Theyare} a good-natured, rambunctious sort, and while \cSci{\they} claim not to look for fights, they sure seem to spend a lot of their port-leave in the infirmary after one ``jolly fight'' or another.
  
  \item \cBoy{\full}, \cBoy{\they}/\cBoy{\them} (\cBoy{\MYplayer}): The newest member of the \pNew{}. \cBoy{\Theywere} picked up at the last port of call for the \pNew{}, where \cBoy{\they} struck up a friendship with \cEng{} and \cNav{}. \cBoy{\Theyare} picking up life aboard \pNew{} quickly, but still seem shy and nervous about messing up.
\end{itemize}

\end{document}
