%%%%%
%%
%% This file sets up the Mem, MemFold, and MemEnvelope datatypes, and
%% creates possible macros for each.
%%
%% The Mem datatype isn't really used directly; it's there so the
%% other datatypes can inherit and share its code.
%%
%%%%%

\DECLARESUBTYPE{Mem}{Element}
\PRESETS{Mem}{
  %% \MYname is the trigger
  \F\MYtext	%%  text
  }


%%%%%
%% MemFold and MemEnvelope are both subtypes of Mem.  MemFold is for
%% fold-n-staple style mempackets, MemEnvelope is for stuff-n-seal
%% style mempackets.  If you want a mempacket to contain interesting
%% contents, like sheets, abilities, and other mempackets, use a
%% MemEnvelope.
\DECLARESUBTYPE{MemFold}{Mem}
\DECLARESUBTYPE{MemEnvelope}{Mem}


%%%%%
%% MemCover and MemPage are for the cover and pages of mempacket
%% booklets, which resemble research notebooks.  These are good
%% substitutes for large piles of MemFolds, and can be useful for
%% things like amnesiac characters.
%%
%% Like MemFolds, MemPages shouldn't directly own any other elements
%% as contents.  Use MemEnvelope instead.
%%
%% MemPages are usually assigned to a MemCover (via \MYmems), with the
%% MemCover representing the entire booklet and assigned to a
%% character.
%%
%% A MemCover is not a mempacket in and of itself; its name is not its
%% trigger and its text is not a memory.
\DECLARESUBTYPE{MemCover}{Mem}
\PRESETS{MemCover}{
  \sd\MYtext	{Each page is a memory/event packet with a separate
		trigger.}
  }

\DECLARESUBTYPE{MemPage}{Mem}


%%%%%
%% \memfold{<trigger>}{<text>}
%% \memenvelope{<trigger>}{<text>}
%% \memcover{<name>}{<pages>}
%% \mempage{<trigger>}{<text>}
%% \startmembook{<name>} <pages> \endmembook
%%
%% These are wrappers around \INSTANCE, useful as 1-shots.
%% \startmembook...\endmembook is a simple wrapper around \memcover
%% that may have better syntax for use within character sheets (inside
%% a \starttag{mems}...\endtag block).
\newinstance{MemFold}{\memfold[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{MemEnvelope}{\memenvelope[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{MemCover}{\memcover[2]}{
  \s\MYname{#1}\s\MYmems{#2}}
\newinstance{MemPage}{\mempage[2]}{
  \s\MYname{#1}\s\MYtext{#2}}

\long\def\startmembook#1#2\endmembook{\memcover{#1}{#2}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{MemFold}{\mTest}{
  \s\MYname	{Test Trigger}
  \s\MYtext	{This is a Test of a fold-n-staple memory packet}
  }
  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Medical RN
\NEW{MemFold}{\mMedOne}{
  \s\MYname	{Medical Officer Research Notebook Page 1 | Trigger 20 minutes after game start.}
  \s\MYtext	{The Captain has confided in you about the apparitions. You suspect they are first contact with a new life form! If only you could see one yourself to study… Set your alpha = 1. || Once you find a ``ghostly figure'' somewhere, trigger your ``Medical Page 2'' mem packet.}
}

\NEW{MemFold}{\mMedTwo}{
  \s\MYname	{Medical Page 2 | Trigger when told to do so.}
  \s\MYtext	{Fascinating. You'll need to run some tests. Unfortunately, the Med Bay doesn't seem to be accessible from where you are. You'll need to get someone to bring you your **Handheld Medical Scanner**. Once you have it, find a **second** ghost. || Once you find a **second** ghost somewhere, trigger your “Medical Page 3” mem packet.}
}

\NEW{MemFold}{\mMedThree}{
  \s\MYname	{Medical Page 3 | Trigger when told to do so}
  \s\MYtext	{Well, whatever these apparitions are, they aren’t human. Get a message to the Diplomat and ask them to help you investigate by **triggering their ``Diplomat 1'' mem packet.** (other players can carry this OOC information for you, along with a reasonable IC message) It may be a little while before they can send an answer back to you; they may not be able to see what you're seeing yet! || The Diplomat will should a message back with which page to open next.}
}

\NEW{MemFold}{\mMedFour}{
  \s\MYname	{Medical Page 4 | Trigger when told to do so.}
  \s\MYtext	{The readings you took while waiting for the Diplomat to answer you don’t agree. I don’t know why your friend would lie to you, but it looks like they did. || After you confront them about this (possibly via proxy), trigger your ``Medical Page 5'' mem packet.}
}

\NEW{MemFold}{\mMedFive}{
  \s\MYname	{Medical Page 5 | Trigger when told to do so.}
  \s\MYtext	{Trigger when told to do so. . You’ll have to go back to the source. Talk to the **Captain** for at least 2 minutes about the apparitions and when they first started seeing the ghosts. Tell them to ** trigger their ``Captain 1'' mem packet** || The Captain will tell you which page to trigger next.}
}

\NEW{MemFold}{\mMedSix}{
  \s\MYname	{Medical Page 6 | Trigger when told to do so.}
  \s\MYtext	{And there's your answer. So disappointing that it isn’t first contact with a new life form. But ghosts of the dead from the battle for the Captain’s home planet, brought forth as the price for the miracle they pulled off by whatever was in that heirloom amulet the Captain smashed isn’t a terrible consolation prize.}
}

\NEW{MemFold}{\mMedSeven}{
  \s\MYname	{Medical Page 7 | Trigger when told to do so.}
  \s\MYtext	{You still don't have all the pieces. How frustrating! You are just trying to help. Maybe you should try asking to Executive Officer? They've known the Captain the longest of anybody. You can also keep leaning on the Captain to try to get the truth.}
}

\NEW{MemFold}{\mDiplomatOne}{
  \s\MYname	{Diplomat 1 | Trigger when told to do so.}
  \s\MYtext	{The Medical Officer is asking you to find a ghost and investigate it somehow. Find something that says you see ``ghostly figures.'' Once you find a place like this, spend 2 minutes there, without doing anything else (other than talking), studying the phenomenon. || Once the time is over, trigger your ``Diplomat 3'' mem packet.}
}

\NEW{MemFold}{\mDiplomatThree}{
  \s\MYname	{Diplomat 3 | Trigger when told to do so.}
  \s\MYtext	{Whatever these are, they aren't a new sentience, so this isn't first contact. You could always lie about it if you feel like being in charge for a while. But can you really do that to your friend? Pass this information back to the Medical Officer in the following way: If you want to tell them this is first contact, tell them so *and* tell them to open "Medical Page 4". If you want to tell them this is NOT first contact, tell them so *and* tell them to open "Medical Page 5". (Other players can carry this OOC information for you, along with an reasonable IC message.)}
}

\NEW{MemFold}{\mCaptainOne}{
  \s\MYname	{Captain 1 | Trigger when told to do so.}
  \s\MYtext	{The Medical officer is clearly interested in the history of the ghosts despite the ongoing crisis. Should you tell them about what really happened? Should you lie? If you choose to tell the truth about what happened on the TMN Pheonix, do so in character, and then instruct them to **trigger their ``Medical page 6 mem packet''**. If you choose to lie, or tell a half truth, do so in character, and then instruct them to **trigger their ``Medical page 7 mem packet''**. Even if you tell them a lie now, you can decide at any time to come clean and tell Medical the truth. If you do so, instruct them to **trigger their ``Medical page 6 mem packet''**.}
}



%%%%%%%%%
%% Science RN
\NEW{MemFold}{\mSciOne}{
  \s\MYname	{Science Officer Research Notebook Page 1 | Trigger 30 minutes after start of game.}
  \s\MYtext	{The Captain has confided in you about the ghosts. You suspect they are **humans from another dimension**. If only you could see one yourself to study\ldots Set your alpha = 1 || Once you find a ``ghostly figure'' somewhere, trigger your ``Science Page 2'' mem packet.}
}

\NEW{MemFold}{\mSciTwo}{
  \s\MYname	{Science Page 2 | Trigger when told to do so.}
  \s\MYtext	{Fascinating. You’ll need to run some tests. Unfortunately, the Science Lab doesn’t seem to be accessible from where you are. You’ll need to get someone to bring you your **handheld science scanner**. Once you have it, find a **second** ghost. || Once you find a **second** ghost somewhere, trigger your ``Science Page 3'' mem packet.}
}

\NEW{MemFold}{\mSciThree}{
  \s\MYname	{Science Page 3 | Trigger when told to do so.}
  \s\MYtext	{Well, whatever these apparitions are, they aren’t from this time and place. You need help from someone else. Didn’t **Weapons** mention seeing ghosts at some point? Get **Weapons** to investigate a ghost. **Tell them to trigger their ``Weapons 1'' mem packet**. || The Weapons Officer will tell you which page to open next. It may take them a little while to get back to you.}
}

\NEW{MemFold}{\mSciFour}{
  \s\MYname	{Science Page 4 | Trigger when told to do so.}
  \s\MYtext	{The additional readings you took while waiting for Weapons to get back to you don’t agree. I don’t know why they would lie to you, but it looks like they did. || After you confront them about this, trigger your ``Science Page 5'' mem packet.}
}

\NEW{MemFold}{\mSciFive}{
  \s\MYname	{Science Page 5 | Trigger when told to do so.}
  \s\MYtext	{You’ll have to go back to the source. Talk to the **Captain** for at least 2 minutes about the apparitions and when they first started seeing the ghosts. Tell them to ** trigger their ``Captain 2'' mem packet** || The Captain will tell you which page to trigger next.}
}

\NEW{MemFold}{\mSciSix}{
  \s\MYname	{Science Page 6 | Trigger when told to do so.}
  \s\MYtext	{And there’s your answer. So disappointing that it isn’t humans from a different dimension. But ghosts of the dead from the battle for the Captain’s home planet, brought forth as the price for the miracle they pulled off by whatever was in that heirloom amulet the Captain smashed isn’t a terrible consolation prize.}
}

\NEW{MemFold}{\mSciSeven}{
  \s\MYname	{Science Page 7 | Trigger when told to do so.}
  \s\MYtext	{You still don't have all the pieces. How frustrating! You are just trying to help. Maybe you should try asking to Executive Officer? They've known the Captain the longest of anybody. You can also keep leaning on the Captain to try to get the truth.}
}

\NEW{MemFold}{\mWeaponsOne}{
  \s\MYname	{Weapons 1 | Trigger when told to do so.}
  \s\MYtext	{The Science officer is asking you to find a ghost and investigate it somehow. Find something that says you see ``ghostly figures.'' Once you find a place like this, spend 2 minutes there, without doing anything else (other than talking), studying the phenomenon. || Once the time is over, trigger your ``Weapons 3'' mem packet.}
}

\NEW{MemFold}{\mWeaponsThree}{
  \s\MYname	{Weapons 3 | Trigger when told to do so.}
  \s\MYtext	{Whatever these are, they aren't humans from another dimension. They look a lot like your nightmares actually. But other people can see them now? They might still be a threat to the ship. You could tell Science that they *are* humans from another dimension, but to what end? | Pass this information back to the Science Officer in the following way: If you want to tell them these ARE humans from another dimension, tell them so *and* tell them to open "Science Page 4". If you want to tell them these are NOT humans from another dimension, tell them so *and* tell them to open "Science Page 5".}
}

\NEW{MemFold}{\mCaptainTwo}{
  \s\MYname	{Captain 2 | Trigger when told to do so.}
  \s\MYtext	{The Science officer is clearly interested in the history of the ghosts despite the ongoing crisis. Should you tell them about what really happened? Should you lie? If you choose to tell the truth about what happened on the TMN Pheonix, do so in character, and then instruct them to **trigger their ``Science page 6 mem packet''**. If you choose to lie, or tell a half truth, do so in character, and then instruct them to **trigger their ``Science page 7 mem packet''**. Even if you tell them a lie now, you can decide at any time to come clean and tell them the truth. If you do so, instruct them to **trigger their ``Science page 6 mem packet''**.}
}

%%%%%%%%%
%% Nav RN
\NEW{MemFold}{\mNavOne}{
  \s\MYname	{Navigation Officer Research Notebook Page 1 | Trigger at start of game.}
  \s\MYtext	{You did it! One of the modifications you made to the engines or the nav must have worked! Well, sort of. You didn’t mean to get the ship stuck like this… You have two goals from here: 1) get some research done before the ship gets fixed, 2) fix the ship so we can survive this. You’ll have to work quickly and try not to get caught! Spend 30 seconds “interacting” with the *damaged* Navigation System in either the “Black” or “Red” dimensions (stay in that channel, don’t engage in activities other than talking - tell people you are investigating the nav system).  You will not be able to make any further progress if you do not investigate the nav system in one of the secondary dimensions **before** it is repaired! || Once you are done interacting with the damaged navigation systems, trigger your “Navigation Page 2” mem packet.}
}

\NEW{MemFold}{\mNavTwo}{
  \s\MYname	{Navigation Page 2 | Trigger when told to do so. }
  \s\MYtext	{Interesting. Normal Jump Navigation requires spherical polar coordinates. You had added a multiplication factor to each coordinate that you thought would direct the ship to the equivalent location in a different dimension. It looks like something is missing though\ldots - Check the scanners in two different locations by spending 2 minutes ``interacting'' with the scanners (stay in that channel, don’t engage in activities other than talking, tell people you are reviewing the scanner outputs). This will allow you to compare the positioning readings and figure out what was missing in the coordinates you input originally. || Once you are done interacting with the scanners, trigger your ``Navigation Page 3'' mem packet.}
}

\NEW{MemFold}{\mNavThree}{
  \s\MYname	{Navigation Page 3 | Trigger when told to do so.}
  \s\MYtext	{Carry the 3… take the arcsine\ldots And there you have it - along with the multiplication factor, you need to include an intercept as well, otherwise the ship doesn’t move completely into the new dimension! Now all you need to do is figure out what numbers you could input as an intercept that correspond to actual other dimensions. You shudder to think what it would mean to ``jump'' to the space between dimensions. - Once the Nav system is fixed, repeat your ``investigation'' (2 minutes in that channel, not doing anything else, tell people you are investigating the nav system). ||  Once you are done interacting with the repaired navigation system, trigger your ``Navigation Page 4'' mem packet.}
}

\NEW{MemFold}{\mNavFour}{
  \s\MYname	{Navigation Page 4 | Trigger when told to do so.}
  \s\MYtext	{And there we go, with the data from the scanners in the two dimensions, and the spherical polar coordinates from the modified and restored nav system, you can deduce a series of likely intercept numbers that *should* correspond to other dimensions!! Go to the ``mechanics-only'' channel, and use the searchcontainer command for ``Packet 1''. Take the 2 items from the packet. Then trigger your ``Navigation page 5'' mem packet.}
}

\NEW{MemFold}{\mNavFive}{
  \s\MYname	{Navigation Page 5 | Trigger when told to do so.}
  \s\MYtext	{You are certain that ``Unusual Coordinates 1'' correspond to your home dimension. You are 90\% certain that ``Unusual Coordinates 2'' correspond to a new dimension. One of these sets of coordinates must make it onto the bridge, in someone's possession, at end of game, so they can enter the coordinates into the ``Navigator Station''. If both sets of coordinates are present on the bridge, characters on the bridge must decide which coordinates to enter.}
}


%%%%%%%%%
%% Threat Assessments
\NEW{MemFold}{\mThreatOne}{
  \s\MYname	{Threat Assessment 1 | Trigger: Open when told to do so.}
  \s\MYtext	{If this isn’t repaired, one of the primary dimensions that overlap to create this secondary dimension won’t re-integrate correctly, and anyone left in that primary dimension won’t survive. The primary dimension that won’t re-integrate will be the one with the fewest people in it. You are not sure that the TMF Hope carries enough supplies to repair everything that needs repair. It may not be possible to save everyone.}
}

\NEW{MemFold}{\mThreatTwo}{
  \s\MYname	{Threat Assessment 2  | Trigger: Open when told to do so.}
  \s\MYtext	{If this isn’t repaired, one of the primary dimensions that overlap to create this secondary dimension won’t re-integrate correctly, and anyone left in that primary dimension won’t survive. The primary dimension that won’t re-integrate will be the one with the fewest people in it. You are not sure that the TMF Hope carries enough supplies to repair everything that needs repair. It may not be possible to save everyone.}
}

\NEW{MemFold}{\mThreatThree}{
  \s\MYname	{Threat Assessment 3  | Trigger: Open when told to do so.}
  \s\MYtext	{If this isn’t repaired, one of the primary dimensions that overlap to create this secondary dimension won’t re-integrate correctly, and anyone left in that primary dimension won’t survive. The primary dimension that won’t re-integrate will be the one with the fewest people in it. You are not sure that the TMF Hope carries enough supplies to repair everything that needs repair. It may not be possible to save everyone.}
}

\NEW{MemFold}{\mThreatFour}{
  \s\MYname	{Threat Assessment 4  | Trigger: Open when told to do so.}
  \s\MYtext	{If this isn’t repaired, one of the primary dimensions that overlap to create this secondary dimension won’t re-integrate correctly, and anyone left in that primary dimension won’t survive. The primary dimension that won’t re-integrate will be the one with the fewest people in it. You are not sure that the TMF Hope carries enough supplies to repair everything that needs repair. It may not be possible to save everyone.}
}

%%%%%%%%%
%% Ghosts in the ship
\NEW{MemFold}{\mBroom}{
  \s\MYname	{Broom Closet  | Trigger: Open when told to do so.}
  \s\MYtext	{There is a ghostly figure dressed as a captain, inside an emergency space suit. It is torn in several places. They say ``You take the last life pod. A good captain goes down with their ship''. They do not respond to you no matter what you try.}
}

\NEW{MemFold}{\mLab}{
  \s\MYname	{Lab Bench  | Trigger: Open when told to do so.}
  \s\MYtext	{ There is a ghostly figure hiding under the bench,covering their heads and muttering about how they should have been a doctor. As you watch, they are consumed by an explosion.}
}

\NEW{MemFold}{\mPatient}{
  \s\MYname	{Patient Bay  | Trigger: Open when told to do so.}
  \s\MYtext	{There is a ghostly figure lying unconscious on the bed in the ward. Their injuries are terrible and consistent with severe shrapnel damage. They do not respond to you no matter what you do.}
}

\NEW{MemFold}{\mKitchen}{
  \s\MYname	{Kitchen  | Trigger: Open when told to do so.}
  \s\MYtext	{There is a ghostly figure huddled in the corner sobbing about lost comrades. Their pearly, translucent skin is covered with cuts and bruises. They do not respond to you no matter what you do.}
}

\NEW{MemFold}{\mWeight}{
  \s\MYname	{Weight Room  | Trigger: Open when told to do so.}
  \s\MYtext	{There is a ghostly figure swearing and frantically trying to repair something you can’t see. They curse and grab a ghostly fire extinguisher. The scene loops back to the beginning.}
}

\NEW{MemFold}{\mTheater}{
  \s\MYname	{Theater  | Trigger: Open when told to do so.}
  \s\MYtext	{A ghostly body in a space suit floats in vacuum, surrounded by debris. You can’t tell if they are unconscious or dead, but the hold in their section of the ship must have been breached by something. They do not respond to you no matter what you do.}
}

\NEW{MemFold}{\mCrates}{
  \s\MYname	{Crates  | Trigger: Open when told to do so.}
  \s\MYtext	{A pair of ghostly figures scramble to load missiles into the missile bays. They hit the ready button, and look at each other with haunted eyes. The scene loops back to the beginning.}
}


%%%%%%%%%%%
%% Alpha Reminders
\NEW{MemFold}{\mCAlpha}{
  \s\MYname	{Alpha | Trigger: Open 10 minutes after game start.}
  \s\MYtext	{Set your Alpha score to 1. If it was already at 1, do not change it. Tell other players you encounter to open their ``Half Way There'' packet.}
}

\NEW{MemFold}{\mXAlpha}{
  \s\MYname	{Alpha | Trigger: Open 40 minutes after game start.}
  \s\MYtext	{Set your Alpha score to 1. If it was already at 1, do not change it. Tell other players you encounter to open their ``Half Way There'' packet.}
}

\NEW{MemFold}{\mDAlpha}{
  \s\MYname	{Alpha | Trigger: Open 50 minutes after game start.}
  \s\MYtext	{Set your Alpha score to 1. If it was already at 1, do not change it. Tell other players you encounter to open their ``Half Way There'' packet.}
}

\NEW{MemFold}{\mWAlpha}{
  \s\MYname	{Alpha | Trigger: Open 60 minutes after game start.}
  \s\MYtext	{Set your Alpha score to 1. If it was already at 1, do not change it. Tell other players you encounter to open their ``Half Way There'' packet.}
}

\NEW{MemFold}{\mAlpha}{
  \s\MYname	{Alpha | Trigger: Open 70 minutes after game start.}
  \s\MYtext	{Set your Alpha score to 1. If it was already at 1, do not change it. Tell other players you encounter to open their ``Half Way There'' packet.}
}

%%Suspicious repairs RN
\NEW{MemFold}{\mRepairsOne}{
  \s\MYname	{Ship Repairs | Trigger: Open if you read a sign that describes the engines or the Navigation system as ``damaged''.}
  \s\MYtext	{ This is bad. Someone messed with the ship's engines, changing them to who knows what purpose. The evidence that the systems were deliberately altered is plain to you as an expert mechanic. No wonder the jump failed. But who? and why? The basic diagnostic program you run gives you ``error code 1433''. You need information about the broken navigation system. Pass the code ``error code 1433'' to the deckhand. You may need to send the message through an intermediary.}
}

\NEW{MemFold}{\mRepairsTwo}{
  \s\MYname	{Code 1433| Trigger: Open if someone or something tells you ``error code 1433''.}
  \s\MYtext	{So both the engines and the navigation system were damaged, and they are both giving the generic error code 1433. You'll have to dig into this. Spend 1 minute BY YOURSELF, with no one else in the room, examining the broken navigation system. If someone comes into the room, start your timer over. | Once the time has elapsed, you receive ``error code 1825.'' You don't know what that code means; you'll need to pass this code to the engineer and hope they do.}
}

\NEW{MemFold}{\mRepairsThree}{
  \s\MYname	{Code 1825| Trigger: Open if someone or something tells you ``error code 1825''.}
  \s\MYtext	{Error code 1825 is a navigation system error code for ``incomplete coordinates.'' The user entry logs show coordinates that match the TMF Hope's jump destination, but the actual hardware of the navigation system seems to have an additional code snippet that adds a multiplication factor to the coordinates. But we already knew this was deliberate. What about the engines? Spend 1 minute BY YOURSELF, with no one else in the room, examining the broken engines. If someone comes into the room, start your timer over. | Once the time has elapsed, you receive ``error code 9997''. You don't remember what that code means; you'll need to pass this code to the deckhand and hope they have been paying attention to your lessons.}
}

\NEW{MemFold}{\mRepairsFour}{
  \s\MYname	{Code 9997| Trigger: Open if someone or something tells you ``error code 9997''.}
  \s\MYtext	{Error codes starting with 999 are crew access codes. They proceed in decreasing order down the chain of command. Did it start indexing at 0 or 1? aka is the captain 9990 or 9991? You can't remember! This means that either Navigation (!) or the Scientist was the crew member who was accessing the engines when they were sabotaged. Better check with the Engineer. Send them ``error code 9990''.}
}

\NEW{MemFold}{\mRepairsFive}{
  \s\MYname	{Code 9990| Trigger: Open if someone or something tells you ``error code 9990''.}
  \s\MYtext	{Error code 9990 is a shipyard code. You knew that kid was good for something. They have reminded you that error codes starting with 999 are crew access codes. They proceed in decreasing order down the chain of command. Indexing starts with 9991 for the Captain. This means that the Navigations Officer is code 9997, and they were the ones was accessing the engines when they were sabotaged! You knew it all along! This is Navigation's fault. Better tell the Captain.  The deckhand will be so disappointed, though; they seemed to get along quite well.}
}

%%%%%%%%% Jury Rig the Intercom  %%%%%%%%%%
\NEW{MemFold}{\mDeckHandOne}{
  \s\MYname	{Deckhand 1| Trigger: Open if you are given a ``Modified Walkie Talkie''.}
  \s\MYtext	{You know, Weapons might be on to something modifying the walkie talkie to reinstate shipboard communication. It still needs a receiver though. Spend 2 minutes in a game space, by yourself, fiddling with the walkie talkie. At the end of this time, go to the ``mechanics-only'' channel, and use the searchcontainer command for ``Packet 3''. Take the ``Modified Receiver'' item from the packet. Pass that item along to the Diplomat.}
}

\NEW{MemFold}{\mDiplomatTwo}{
  \s\MYname	{Diplomat 2 | Trigger: Open if you are given a 	``Modified Receiver''.}
  \s\MYtext	{Technology isn't really your strong suit, but communication is. And you are very interested in getting ship wide communication going again. Spend 2 minutes in a game space, by yourself, fiddling with the modified receiver. At the end of this time, go to the "mechanics-only" channel, and use the searchcontainer command for ``Packet 4''. Take the "Modified Intercom Interface" item from the packet. Pass that item along to the Engineer to install it.}
}

\NEW{MemFold}{\mEngineerOne}{
  \s\MYname	{Engineer 1 | Trigger: Open if you are given a 	``Modified Intercom Interface''.}
  \s\MYtext	{Of all the places you expected a clever engineering solution from, it was not Weapons, or the Diplomat. Must be the good influence of the Deck Hand. Still, if you install this in ``Ships Intercom'' in the Medical Bay, you should be able to restore some form of communication across the whole ship. It will be painfully slow, only able to carry messages from each user once per 10 minutes. You'll need the Weapons officer's help to install it though, and working that closely together they will surely learn about your bad eyesight. To install the "Modified Intercom Interface", spend 2 minutes ``working'' with the weapons officer (2 minutes  in that channel, not doing anything else but talking, tell people you are messing with the intercom when they enter the space.) | At the end of that time: 1) Drop the ``Modified Intercom Interface'' into the ``Ships Intercom'' container, 2) Tell Weapons to open their ``Weapons 2'' mem packet now, 3) @ the GM in the med-bay text channel with the message ``Modified Intercom Installed.'' The GMs will handle bringing the intercom online.}
}

\NEW{MemFold}{\mWeaponsTwo}{
  \s\MYname	{Weapons 2 | Trigger: Open when told to do so by a player}
  \s\MYtext	{There's something wrong with the Engineer's eyes. Seriously wrong. You hadn't been able to pin it before, but working so closely to install the ``Modified Intercom Interface'' made it undeniable. Do you need to tell somebody that your engineer is nearly blind?}
}

\NEW{MemFold}{\mPractice}{
  \s\MYname	{Practice | Trigger: Open when the Playground instructions tell you to}
  \s\MYtext	{You openend a mem-packet. Yay! Remember, the bot sends mem-packet messages to your Direct Messages.}
}
