\documentclass[green]{TMFHope}
\parindent=0pt
\begin{document}
\name{\gFixTheShip{}}

Fixing the \pNew{} is crucial to getting out of this mess alive. The ship can only survive 2 hours of strain, being split between dimensions like this. At the 2 hour mark, the ship's auto-pilot will try to reverse out of this mess. \emph{OOC Note: By unanimous vote of the players (not the characters), you may engage the reversal sooner and end the LARP early.}

Before that timer runs out, you will need to repair as much of \pNew{} as you can. 
\begin{itemize}
  \item The \textbf{engines} and the \textbf{navigation sensor system} are both damaged, each in two different places. The access points for them will need to be discovered - very little is where you might expect due to the bending of space in and around the ship. 
  \item Each access point will list the supplies required to repair it, which you will need to find. 
	\item They will all also require use of a \textbf{\iTorch{\MYname{}}}, of which the \pNew{} carries only one, so it will need to be passed around.  Note that the \iTorch{\MYname{}} has a five-minute cooldown, which you must monitor yourself when using it.  If you hand off the \iTorch{\MYname{}} to someone else, have them start a timer for whatever time was left in the cooldown.
	\item Repairs can only be initiated by someone with the ``Engineer'' ability.
\end{itemize}
Since \pNew{} is a small freighter, traveling well known, safe, transport lines, it does not carry very many spare parts - \textbf{there may not be enough supplies to repair every piece of damage.}\\

This might be problematic if un-repaired damage puts part of the crew in danger. Luckily, the \pNew{}, like all modern ships, is equipped with basic teleporter technology. There is no planet or other ship within range that someone could be teleported to, but with the proper authorization, the teleporter can be used to move someone from one part of the ship to another - and thus from one dimension to another.

\begin{itemize}
  \item The teleporter can be reached from any \sConsole{} (available in the primary dimensions).
  \item A \iCrystal{\MYname{}} must be installed in the console.
	\item The console must be activated by someone holding an \iKey{\MYname{}}.
	\item The teleporter can only be used to teleport other people - you cannot teleport yourself.
	\item You and the person you are teleporting away must be in the same game space as the \sConsole{}, and each other.
	\item Details for this operation are available on the \sConsole{} container itself.
\end{itemize}
\textbf{Caution:} While this technology is generally accessible across the ship, the \pNew{} carries \textbf{very few} of these \iCrystal{\MYname{}}s. They should be used with the utmost judiciousness. 

\emph{OOC Note: even ``optimal'' use of all available mechanics to repair the ship may not allow every character to survive.}

\end{document}
